Viscous Erosion in Porous Media

### 2018-01-30 docs/methods/erosion_methods.tex
NM

Now, the body's rate of area reduction is given by integrating the absolute shear stress around the boundary
\begin{equation}
\dot{A} = \int_{\gamma} \atau \, ds \, ,
\end{equation}
giving the exact relationship
\begin{equation}
\dot{A} = \mean{\atau} L \, .
\end{equation}
Thus, the area-loss rate is given by the product of the mean shear $\mean{\atau}$ and the total perimeter $L$. Inserting the scaling law \eqref{eq:stresslaw} gives
 \begin{equation}
\dot{A} \sim \frac{\mu \umax}{\log(W/L)} \, .
\end{equation}
Noting that $A \sim L^2$ allows one to solve the ODE to determine how the body area changes with time
\begin{equation}
A (1 - \log A) = \areaconst (t_f - t)
\end{equation}
This is an {\em implicit} relationship for how the area scales down in time during erosion.

\todo[inline]{Define $\areaconst$; also maybe need to use a different letter.}

In Fig.~6a, we show the body area vs time measured in the simulation
against the above scaling law. In the scaling law, we chose, $\areaconst = 0.42$
(check this?)

@@

>>>>

Now, the body's rate of area reduction is given by integrating the absolute shear stress around the boundary
\begin{equation}
\dot{A} = \int_{\gamma} \atau \, ds \, ,
\end{equation}
giving the exact relationship
\begin{equation}
\dot{A} = \mean{\atau} L \, .
\end{equation}
Thus, the area-loss rate is given by the product of the mean shear $\mean{\atau}$ and the total perimeter $L$. Inserting the scaling law \eqref{eq:stresslaw} gives
 \begin{equation}
\dot{A} \sim \frac{\mu \umax}{\log(W/L)} \, .
\end{equation}
Noting that $A \sim L^2$ allows one to solve the ODE to determine how the body area changes with time
\begin{equation}
A (1 - \log A) = \areaconst (t_f - t)
\end{equation}
where $c_A$ is a constant.
This is an {\em implicit} relationship for how the area scales down in time during erosion.
In Fig.~6a, we show the body area as a function of time measured in the simulation
against the above scaling law with $\areaconst = 0.42$.

@@

We aim to measure the opening angle in our simulation, but, curiously, the body vanishes before a steady-state is definitively reached. To obtain the true terminal shape, we could restart our simulation with the final eroded body scaled up and iterate this process until reaching steady state. A simpler solution, though, is to remove the effect of shrinking during the erosion process by simply modifying the normal velocity $\Vn$ to have zero mean
